---
title: "data_direcotry"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE, echo=FALSE}
Sys.setenv("LOG_LEVEL" = "INFO")
source("run_analysis.R")
```

## df_clean

| Variable            | Description                                                                                                         |
|---------------------|---------------------------------------------------------------------------------------------------------------------|
| set                 | The original dataset it came from: "test", "train"                                                                  |
| participant         | The participant number obtained from the raw data                                                                   |
| activity            | The descriptive activity name: "LAYING", "SITTING", "STANDING", "WALKING", "WALKING_DOWNSTAIRS", "WALKING_UPSTAIRS" |
| mean_value          | The mean value obtained for the measurement                                                                         |
| measurement         | The type of measurement: "mean", "std"                                                                              |
| dimension           | The dimension/axis of the original signal: "X", "Y", "Z"                                                            |
| acceleration_signal | An indication whether the acceleration signal was a body or gravity acceleration signals: "Body", "Gravity"         |
| sensor_signal       | An indication whether the signals come from the accelerometer or gyroscope: "Acc", "Gyro"                           |
| jerk_signal         | An indication whether the mean_value has been transformed into a jerk signal: "yes", NA                             |
| magnitude           | An indication whether the magnitude has been derived for this mean_value: "yes", NA                                 |
| time_signal         | Indication whether the mean_value concerns a time domain signal: "yes", NA                                          |
| frequency_signal    | Indication whether the mean_value concerns a time frequency signal: "yes", NA                                       |

The df_clean dataframe is the final form of the transformed data and is a long form of the original data. In this data frame both training and test data observations are contained.

Number of observations :

```{r message=FALSE, warning=FALSE, echo=FALSE}
print(nrow(df_clean))
```

```{r message=FALSE, warning=FALSE, echo=FALSE}

library(dplyr)
library(knitr)

df_describeclean <- data.frame(variable = names(df_clean))
description_values <- "The mean of the original raw data observations"
for(i in df_describeclean$variable){if(i == "mean_value"){df_describeclean$value[df_describeclean$variable == i] <- description_values}else{df_describeclean$value[df_describeclean$variable == i] <- distinct(df_clean[i])}}

kable(df_describeclean)
```

## df_test 

Contains the data from the "./data/UCI HAR Dataset/test/X_test.txt" file

```{r message=FALSE, warning=FALSE, echo=FALSE}
print(str(df_test))
```

## df_train

Contains the data from the "./data/UCI HAR Dataset/train/X_train.txt" file

```{r message=FALSE, warning=FALSE, echo=FALSE}
print(str(df_train))
```

## df_merged

After some manipulations the data from df_test and df_train is merged into df_merged.

```{r message=FALSE, warning=FALSE, echo=FALSE}
print(str(df_merged))
```

## activity_labels

Contains the data from the "./data/UCI HAR Dataset/activity_labels.txt" file

```{r message=FALSE, warning=FALSE, echo=FALSE}
kable(activity_labels)
```

## feature_names

Contains the data from the "./data/UCI HAR Dataset/features.txt" file

Explanation from the source data : "*The features selected for this database come from the accelerometer and gyroscope 3-axial raw signals tAcc-XYZ and tGyro-XYZ. These time domain signals (prefix 't' to denote time) were captured at a constant rate of 50 Hz. Then they were filtered using a median filter and a 3rd order low pass Butterworth filter with a corner frequency of 20 Hz to remove noise. Similarly, the acceleration signal was then separated into body and gravity acceleration signals (tBodyAcc-XYZ and tGravityAcc-XYZ) using another low pass Butterworth filter with a corner frequency of 0.3 Hz.*

*Subsequently, the body linear acceleration and angular velocity were derived in time to obtain Jerk signals (tBodyAccJerk-XYZ and tBodyGyroJerk-XYZ). Also the magnitude of these three-dimensional signals were calculated using the Euclidean norm (tBodyAccMag, tGravityAccMag, tBodyAccJerkMag, tBodyGyroMag, tBodyGyroJerkMag).*

*Finally a Fast Fourier Transform (FFT) was applied to some of these signals producing fBodyAcc-XYZ, fBodyAccJerk-XYZ, fBodyGyro-XYZ, fBodyAccJerkMag, fBodyGyroMag, fBodyGyroJerkMag. (Note the 'f' to indicate frequency domain signals).*

*These signals were used to estimate variables of the feature vector for each pattern:*

*'-XYZ' is used to denote 3-axial signals in the X, Y and Z directions.*" (Jorge L. Reyes-Ortiz, Alessandro Ghio, Luca Oneto, Davide Anguita. November 2012.)

```{r message=FALSE, warning=FALSE, echo=FALSE}
print(summary(feature_names))
print("Overview")
print(str(feature_names))
```

## test_labels

Contains the data from the "./data/UCI HAR Dataset/test/y_test.txt" file and refers to the activity IDs of the participants.

```{r message=FALSE, warning=FALSE, echo=FALSE}
print(summary(test_labels))
print("Overview")
print(str(test_labels))
```

## test_participants

Contains the data from the "./data/UCI HAR Dataset/test/subject_test.txt" file.

```{r message=FALSE, warning=FALSE, echo=FALSE}
print(summary(feature_names))
print("Overview")
print(str(feature_names))
```

## train_labels

Contains the data from the "./data/UCI HAR Dataset/train/y_train.txt" file and refers to the activity IDs of the participants.

```{r message=FALSE, warning=FALSE, echo=FALSE}
print(summary(train_labels))
print("Overview")
print(str(train_labels))
```

## train_participants

Contains the data from the "./data/UCI HAR Dataset/train/subject_train.txt" file.

```{r message=FALSE, warning=FALSE, echo=FALSE}
print(summary(train_participants))
print("Overview")
print(str(train_participants))
```
